Verifying Demonstrations

### 2018-05-24 paper/properties.tex
Updates privacy requirements in properties.tex

This leaves us with what should correspond to vote privacy.
We need unlinkability between Alice's identity and Alice's participation proof.
Given a participation proof, Grace will not be able to tell if it belongs to 
Alice or Bob.
This is stronger than vote privacy, where Grace may know that Alice voted but 
not what she voted, whereas here she may not know whether Alice \enquote{voted} 
or not.
Thus participants and non-participants must be indistinguishable.
As this is quite difficult to achieve, we settle for something slightly weaker:
\begin{requirements}[P]
\item\label{ProtestInd} Participants of two different protests must be 
  indistinguishable.
\end{requirements}
Thus Alice can always argue to be part of any counter-protest while actually 
supporting the protest, which, in fact, is a slight increase in privacy over 
ordinary protests.

>>>>

This leaves us with what should correspond to vote privacy.
We need unlinkability between Alice's identity and Alice's participation proof.
Given a participation proof, Grace will not be able to tell if it belongs to 
Alice or Bob.
Furthermore, if Grace has managed to link one proof to Alice's, she should not 
be able to link another proof as a consequence.
Hence, we can summarize our needed properties as follows:
\begin{requirements}[P]
\item\label{ProofUnlink} Participants must be unlinkable to their proofs.
\item\label{ProtestUnlink} Participants (or proofs for the same participant) 
  must be unlinkable between different protests.
\end{requirements}
Thus Alice can always argue to be part of the protest in Grace's favour instead 
of any protest against Grace, which, in fact, is a slight increase in privacy 
over ordinary protests.
